TRIAD: Towards Real-time, Interactive Analysis of Data

### 2015-05-01 paper.tex
changed to use package enumitem. Began editing text.

\usepackage{mathptmx}
\usepackage{graphicx}
\usepackage{times}
\usepackage{multibib}
\newcites{orgref}{Publications by Organizers}
\newcites{ref}{Other References}

@@

In the current design of database and analytics systems, interactive
data analysis concerns are usually an afterthought. Although recent
architectural changes like columnar databases have enabled faster
visualization systems, these sorts of innovations have been designed
less for visualization than for accelerating queries in general. In
this workshop, we will explore the consequences of pushing the
concerns of interactive data analysis deep into the ``computational
fabric'' of our systems: the back-end infrastructure of data storage,
organization, and retrieval. If we design with the knowledge that
every analysis is eventually read by a human, bound by perceptual
limitations and latency constraints, what are the consequences for
database design, or data analysis and visualization algorithms? Are
there fundamental tradeoffs? What can we give up?

@@

As noted earlier, it is our hope that this workshop will include both
attendees from the VIS and database communities. However, since the
workshop will be located at VIS, we will specifically reach out to
members of the database community and invite them to attend the
workshop. We will seek a mix of researchers in different stages of
their careers, together with researchers from different companies in
the industry. If possible, we will also seek to identify a more senior
person from this invited list as the keynote speaker for the workshop.\\

\noindent \textbf{Senior researchers}:
\begin{itemize}
\setlength\itemsep{0em}
\item Sam Madden (MIT)
\item Joe Hellerstein (Berkeley, Trifacta)
\item Mike Stonebraker (MIT)
\item Ugur Cetintemel (Brown)
\item Stan Zdonik (Brown)
\end{itemize}

\noindent \textbf{Early or mid-career researchers}:
\begin{itemize}
\setlength\itemsep{0em}
\item Eugene Wu (Columbia)
\item Aaron Elmore (U. Chicago)
\item Joey Gonzalez (Berkeley AMPLab, CMU, GraphLab/Dato)
\item Bill Howe (UW)
\item Arnab Nandi (OSU)
\item Cecilia Aragon (UW; astronomy/scivis background)
\item Jenny Duggan (Northwestern)
\item Mike Cafarella (Michigan)
\end{itemize}

\noindent \textbf{Junior Researchers (Students, etc.)}: 
\begin{itemize}
\setlength\itemsep{0em}
\item Manasi Vartak (MIT, SeeDB)
\item Todd Mostak (MapD)
\item Leilani Battle (MIT, Tile Prefetching)
\item Dominik Moritz (UW)
\item Holger Pirk (MIT postdoc, databases)
\end{itemize}

\noindent \textbf{Relevant companies we will reach out to}:
\begin{itemize}
\setlength\itemsep{0em}
\item Tableau
\item Trifacta
\item Paradigm4
\item Graphistry
\end{itemize}

>>>>

\usepackage{mathptmx}
\usepackage{graphicx}
\usepackage{times}
\usepackage{enumitem}
\usepackage{multibib}
\newcites{orgref}{Publications by Organizers}
\newcites{ref}{Other References}

@@

In the current design of database and analytics systems, interactive
data analysis concerns are usually an afterthought. Although recent
architectural changes like columnar databases have enabled faster
visualization systems, these databases are often not specified optimized for data visualization purposes but for general acceleration of queries. In
this workshop, we will explore the consequences of pushing the
concerns of interactive data analysis deep into the ``computational
fabric'' of our systems: the back-end infrastructure of data storage,
organization, and retrieval. If we design with the knowledge that
every analysis is eventually read by a human, bound by perceptual
limitations and latency constraints, what are the consequences for
database design, or data analysis and visualization algorithms? Are
there fundamental tradeoffs? What can we give up?

@@

As noted earlier, it is our hope that this workshop will include both
attendees from the VIS and database communities. However, since the
workshop will be located at VIS, we will specifically reach out to
members of the database community and invite them to attend the
workshop. We will seek a mix of researchers in different stages of
their careers, together with researchers from different companies in
the industry. If possible, we will also seek to identify a more senior
person from this invited list as the keynote speaker for the workshop.

\subsection*{Senior researchers}
\begin{itemize}[topsep=0pt, partopsep=0pt, itemsep=-3pt]
\item Sam Madden (MIT)
\item Joe Hellerstein (Berkeley, Trifacta)
\item Mike Stonebraker (MIT)
\item Ugur Cetintemel (Brown)
\item Stan Zdonik (Brown)
\end{itemize}

\subsection*{Early or mid-career researchers}
\begin{itemize}[topsep=0pt, partopsep=0pt, itemsep=-3pt]
\item Eugene Wu (Columbia)
\item Aaron Elmore (U. Chicago)
\item Joey Gonzalez (Berkeley AMPLab, CMU, GraphLab/Dato)
\item Bill Howe (UW)
\item Arnab Nandi (OSU)
\item Cecilia Aragon (UW; astronomy/scivis background)
\item Jenny Duggan (Northwestern)
\item Mike Cafarella (Michigan)
\end{itemize}

\subsection*{Junior Researchers (Students, etc.)}
\begin{itemize}[topsep=0pt, partopsep=0pt, itemsep=-3pt]
\item Manasi Vartak (MIT, SeeDB)
\item Todd Mostak (MapD)
\item Leilani Battle (MIT, Tile Prefetching)
\item Dominik Moritz (UW)
\item Holger Pirk (MIT postdoc, databases)
\end{itemize}

\subsection*{Relevant companies we will reach out to}
\begin{itemize}[topsep=0pt, partopsep=0pt, itemsep=-3pt]
\item Tableau
\item Trifacta
\item Paradigm4
\item Graphistry
\end{itemize}
